### 2021-03-09 text/draft.tex
update conclusion

Edoc is the institutional repository of the University of Basel. It runs
on the EPrints 3 document management system
(https://github.com/eprints/eprints). Edoc was conceived in 2009 as
repository for electronic dissertations and grew in scope when the
University of Basel adapted its first open access policy in 2013. Today
Edoc contains roughly 68'000 items, most of them journal articles
without full text support. Even though descriptive and administrative
metadata are collected for each item, this does not include subject
terms. The lack of subject indexing hampers the repository's usability
and potential with respect to the topic-based monitoring of research
output and, to a lesser extent, information retrieval. The goal of this
project is to remedy this situation with the help of machine indexing.

!! More precisely, this project aims to provide a roadmap for indexing
the elements of Edoc with Annif (Suominen, 2018) -- an open source tool
for automated subject indexing and classification -- and BARTOC FAST
(Hindermann and Ledl, 2020), a federated asynchronous search tool that
covers concepts of thousands of knowledge organization systems like
thesauri, classifications etc.

!! The goal of this thesis is to investigate to what extent machine
indexing can be used to ameliorate institutional repositories.

@@

The focus of this project lies primarily on practical implementation of
the prototype although care is taken to spell out design decisions in as
much detail as is needed. All code written and data generated during the
process of implementing the prototype is available at
\url{https://github.com/MHindermann/mas}:

@@

To analyse the spread of keywords in the sample data set, the keywords
per item are counted. To do so, we call \texttt{Keywords.make\_count} on
\texttt{/indexed/indexed\_master\_mesh\_enriched.json} and save the
output as \texttt{/analysis/keywords\_counted.json}:

@@

In \protect\hyperlink{general-results}{section ``General results''} I
have identified and discussed the overall best Annif configerations.
However, in \protect\hyperlink{analysis}{section ``Analysis''}, I had
noted the caveat that the performance of Annif might vary according to
department due to systematic biases in constructing the Edoc sample data
set. In this section I will therefore assess the performance of the
various Annif configurations per department.

@@

\hypertarget{recommendation}{%
\subsection{Recommendation}\label{recommendation}}

Answer some questions asked in the proposal. Briefly summarize results.
Recommend using Out of the box annif for production. sketch
implementation strategy.

\hypertarget{further-research}{%
\subsection{Further research}\label{further-research}}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  mesh. mesh; A gold standard is usually the product of manual indexing
  by ``information experts, subject experts, or potential or real end
  users'' (Golub et al. 2016, 10). This entails its own host of
  epistemic problems relating to objectivity and consistency of the
  assigned subject terms. Most importantly, however, the construction of
  a gold standard from scratch is very expensive. It is therefore not an
  option for the project at hand. Rather, I will construct what could be
  called derivative gold standards by reusing indexing data that is
  already available. Here we can distinguish two distinct kinds of
  derivative gold standards: first, I will construct a derivative gold
  standard based on the author keywords available in the sample data
  set; call this the ``derivative'' gold standard. Second, I will
  construct a derivative gold standard based on indexing metadata
  available in repositories distinct from Edoc; call this the
  ``foreign'' gold standard. / We enrich the sample items with MeSH
  keywords from PubMed if available (item needs a PubMed ID and items
  needs to be indexed with MeSH on PubMed, 1653 items match this
  requirement); the resulting file is indexed\_master\_mesh.json. Like
  so: Data.enrich\_with\_mesh(DIR + ``/indexed/indexed\_master.json,''
  DIR + ``/indexed/indexed\_master\_mesh'')
\item
  full text
\item
  german vocabulary
\item
  select domain specific vocabularies with bartoc suggest
\end{enumerate}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Gantert.2016}{}%
Gantert, Klaus. 2016. \emph{Bibliothekarisches Grundwissen}. 9.,
vollst{ä}ndig neu bearbeitete und erweiterte Auflage. Berlin: {De
Gruyter Saur}. \url{https://doi.org/10.1515/9783110321500}.

@@

>>>>

Edoc is the institutional repository of the University of Basel. It runs
on the EPrints 3 document management system (see
\url{https://github.com/eprints/eprints}). Edoc was conceived in 2009 as
repository for electronic dissertations and grew in scope when the
University of Basel adapted its first open access policy in 2013. In
early 2021, Edoc contained roughly 68'000 items, most of them journal
articles without full text support. Even though descriptive and
administrative metadata are collected for each item, this does not
include subject terms. The lack of subject indexing hampers the
repository's usability and potential with respect to the topic-based
monitoring of research output and, to a lesser extent, information
retrieval. The goal of this project is to remedy this situation with the
help of machine indexing.

@@

The focus of this project lies primarily on practical implementation of
the prototype although care is taken to spell out design decisions in as
much detail as is needed. All code written and data generated during the
process of implementing the prototype is available at
\url{https://github.com/MHindermann/mas} and comes in three categories:

@@

To analyse the spread of keywords in the sample data set, the keywords
per item are counted. To do so, we call \texttt{Keywords.make\_count} on
\texttt{/indexed/indexed\_master.json} and save the output as
\texttt{/analysis/keywords\_counted.json}:

@@

In \protect\hyperlink{general-results}{subsection ``General results''} I
have identified and discussed the overall best Annif configerations.
However, in \protect\hyperlink{sample-data-set}{section ``Sample data
set''}, I had noted the caveat that the performance of Annif might vary
according to department due to systematic biases in constructing the
Edoc sample data set. In this section I will therefore assess the
performance of the various Annif configurations per department.

@@

!! improve data collection of keywords

!! Answer some questions asked in the proposal. Briefly summarize
results. Recommend using Out of the box annif for production. sketch
implementation strategy.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  In response to the result that increasing the text basis to titles and
  abstracts does not increase performance discussed in
  \protect\hyperlink{assessment}{section ``Assessment''}, add full text
  support and evaluate the performance by increasing the text basis even
  further. To do this, \texttt{Data.enrich\_with\_annif} must be amended
  to fetch and parse the full text PDFs. For an item in the sample data
  set, the link to the full text is constructed from the data fields
  \texttt{offical\ url} and \texttt{documents\ -\ main}. Initial tests
  using the Tika Python library for parsing were promising.
\item
  Originally I had intended to undertake an additional performance test
  based on a gold standard distinct from the derivative gold standard
  constructed in \protect\hyperlink{gold-standard}{section ``Gold
  standard''}. In order to do so, items in the Edoc sample data set were
  enriched with MeSH terms (see
  \url{https://www.nlm.nih.gov/mesh/meshhome.html}) retrieved from
  PubMed (if they had a PubMed ID). This was achieved by calling
  \texttt{Data.enrich\_with\_mesh} on
  \texttt{/indexed/indexed\_master.json}. However, the Annif API does
  not include a configuration with a MeSH vocabulary, and there is no
  concordance between MeSH and either Wikidata or YSO (see
  \url{https://coli-conc.gbv.de/cocoda/app/concordances.html}).
  Therefore, the MeSH terms obtained from PubMed would have to be
  reconciled with Wikidata and YSO in a very time-consuming manner,
  yielding again only a derivative gold standard. As a way forward, it
  would be more effective to train a local instance of Annif on the
  already obtained MeSh data.
\item
  As shown in \protect\hyperlink{assessment}{section ``Assessment''},
  the performance of Annif configurations varies with department. It is
  hence plausible that some (subsets of) items in Edoc require
  domain-specific vocabularies that are not available in Annif. These
  vocabularies can be identified using BARTOC FAST (Hindermann and Ledl
  2020); the implementation is straightforward with my bartocsuggest
  Python library that already includes an Annif wrapper (see
  \url{https://pypi.org/project/bartocsuggest/}).
\item
  An issue that has been neglected in this project is the fact that Edoc
  is a multilingual repository containing more than 3'324 items in
  German (roughly 5\% of Edoc) and 273 items in other languages (less
  than 0.5\% of Edoc).\footnote{The Edoc sample data set only contains
    53 non-English (inclduding 48 German) items; the negligence is hence
    well justified.} Here it would be interesting to train a local
  instance of Annif with GND similar in spirit to Nagelschmidt
  (12.11.2020) and compare its perfomance to other machine indexing
  tools such as DA-3 (Beckmann et al. 2019) which are currently
  informally evaluated at the University Library Basel.
\end{enumerate}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Beckmann.2019}{}%
Beckmann, Regine, Imma Hinrichs, Melanie Janßen, Gérard Milmeister, and
Peter Schäuble. 2019. {``Digitale Assistent DA-3.''} \emph{O-Bib. Das
Offene Bibliotheksjournal} 6 (3): 1--20.
\url{https://doi.org/10.5282/O-BIB/2019H3S1-20}.

\leavevmode\hypertarget{ref-Gantert.2016}{}%
Gantert, Klaus. 2016. \emph{Bibliothekarisches Grundwissen}. 9.,
vollst{ä}ndig neu bearbeitete und erweiterte Auflage. Berlin: {De
Gruyter Saur}. \url{https://doi.org/10.1515/9783110321500}.

@@

\leavevmode\hypertarget{ref-Hindermann.2020}{}%
Hindermann, Maximilian, and Andreas Ledl. 2020. {``BARTOC FAST: A
Federated Asynchronous Search Tool for Remote Vocabulary Access.''} In
\emph{Knowledge Organization at the Interface}, edited by Marianne
Lykke, Tanja Svarre, Mette Skov, Daniel Martínez-Ávila, and
International Society for Knowledge Organziation International Society
for Knowledge Organziation, 200--206. Advances in Knowledge
Organization. Baden-Baden: {Ergon -- ein Verlag in der Nomos
Verlagsgesellschaft}. \url{https://doi.org/10.5771/9783956507762-200}.
